### 2012-02-19 Rctl/inst/doc/manual.Rnw
Moved the R page into Rctl folder

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Danny Arends
% The qcl mapping routine
%\VignetteIndexEntry{Manual}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt]{article}

@@

\begin{center}
\vspace*{1in}
\textbf{\Large QCL mapping in R }

@@

\textbf{\sffamily Abstract}: Introduction into quanitative correlation 
locus (QCL) mapping using the R package qcl
\vfill

@@

\textbf{\sffamily QCLscan and QCLscan.network}
\nopagebreak

Explains how to map QCL using the QCLscan and QCLscan.network functions.

\bigskip
\textbf{\sffamily Significance using QCLpermute}
\nopagebreak

Explains how to determine QCL significance using the QCLpermute function.

\bigskip
\textbf{\sffamily Advanced plots and QCL networks}
\nopagebreak

@@

\newpage
{\small
\noindent \textbf{\sffamily Package qcl function overview} \\
\noindent \begin{tabular}{ll} 
\hspace*{25mm} & \hspace*{103mm} \\ \hline
QCLscan & Genome wide scan for QCL \\
QCLscan.network & Scan for QCL using start gene(s) \\
QCLpermute & Significance thresholds for QCL by permutation \\
plot.QCL & Plot QCL profiles at increasing cut-offs \\
image.QCL & Image a multiple phenotype scan \\
\hline
\end{tabular}
}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Danny Arends
% The ctl mapping routine
%\VignetteIndexEntry{Manual}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt]{article}

@@

\begin{center}
\vspace*{1in}
\textbf{\Large CTL mapping in R }

@@

\textbf{\sffamily Abstract}: Introduction into quanitative correlation 
locus (CTL) mapping using the R package CTL
\vfill

@@

\textbf{\sffamily CTLscan and CTLscan.network}
\nopagebreak

Explains how to map CTL using the CTLscan and CTLscan.network functions.

\bigskip
\textbf{\sffamily Significance using CTLpermute}
\nopagebreak

Explains how to determine CTL significance using the CTLpermute function.

\bigskip
\textbf{\sffamily Advanced plots and CTL networks}
\nopagebreak

@@

\newpage
{\small
\noindent \textbf{\sffamily Package CTL function overview} \\
\noindent \begin{tabular}{ll} 
\hspace*{25mm} & \hspace*{103mm} \\ \hline
CTLscan & Genome wide scan for CTL \\
CTLscan.network & Scan for CTL using start gene(s) \\
CTLpermute & Significance thresholds for CTL by permutation \\
plot & Plot CTL profiles at increasing cut-offs \\
image & Image a multiple phenotype scan \\
\hline
\end{tabular}
}
